% !TeX program = xelatex
% !BIB program = biber
\documentclass[12pt,letterpaper]{article}
\input{preamble.tex} % Packages and settings
\fancyhead[R]{Last \thepage}

\begin{document}

\noindent First Last\\
\noindent Professor\\
\noindent Aesthetics and Imagination\\
\noindent 19 April 2026

% Center environment adds unwanted vertical padding
{\centering Art, Cognition, and Entangled Domains\par}

% --- Content ---

In \textit{The Entanglement}, Alva Noë applies and develops the concept of
``entanglement''; concluding, at one point, that ``Art and philosophy are
entangled with life and science'' \autocite[202]{noeEntanglement2023}. Here, I
argue that this entanglement is broader than the particular fields Noë mentions;
individual disciplines or concepts are not the only kinds of things subject to
the entanglement. Instead, entire domains or spheres of human existence are
entangled. In particular, using the work of Hannah Arendt and Byung-Chul Han, I
develop the concept of an exclusive sphere that stands outside the public realm
of common human affairs. These two spheres turn out to be entangled; moreover,
this political entanglement can explain when and how the exclusive becomes
politically salient.

In my analysis, I focus on art, cognitive science, and the cognitive science of
art. How each item relates to the political realm (that is, whether it respects
its entanglement) predicts its political power. At times, my interpretation of
the entanglement differs from Noë's. Regardless, the points we share are
fundamental to the entanglement. These points are exemplified by the
entanglement of dance (a common, ``habitual'' activity, in Noë's terms) and
Dance (an artistic practice related to choreography).

Lowercase ``dance,'' as Noë describes it, is an ostensibly naïve and
unencumbered activity; dancing is doing what feels right in the moment.
Moreover, dance is habitual in the sense that, to ``the degree to which we
excel, we do so by letting ourselves go'' \autocite[27]{noeEntanglement2023}.
Noë's concept of habit is slightly idiosyncratic; it concerns an automatic way
of being that is more susceptible to inclination. This authentic, habitual way
of being is what Noë calls the first-order self
\autocite[19]{noeEntanglement2023}.  By contrast, uppercase ``Dance'' (or
choreography) involves our second-order selves. Dance requires reflection on
dance so that it may put the latter on display and investigate it
\autocite[29]{noeEntanglement2023}. Thus, Dance requires us to distance
ourselves from the initially familiar act of dancing.

It is worth noting the role of distance in the relationship between dance and
Dance. In \textit{The Entanglement}, this concept is hardly central, but I will
later argue that it is essential for a politically salient entanglement. For
Han, ``Respect presupposes a distanced look''; to respect something is, in part,
to distance yourself from it. Han contrasts respect with ``spectacle,'' a kind
of ``voyeuristic gazing'' without deference \autocite[1]{hanSwarm2017}. When one
engages in Dance, they remove themselves from the immediacy of dance while
keeping it as their focus. This sort of healthy looking, I argue, is essential
to the broader entanglements discussed down the line.

% point out two things: first and second order are bi-directional and first not
% naive also, does not eliminate differences between entangled concepts
Returning to dance and Dance, it is crucial to recognize that the relationship
between first- and second-order acts is bi-directional. While the first-order
gives the second-order its substance, the second-order also alters the first.
When one dances, they do so intuitively; nonetheless, dancing calls on
choreography. Individual dance moves, as well as the norms governing what
constitutes dance, will, in part, come from choreography or Dance
\autocite[30]{noeEntanglement2023}. In short, the first-order act of dancing was
not naïve or fully natural. Regardless, the entanglement does not collapse the
conceptual distinction between dance and choreography; in fact, Noë argues that
this conceptual distinction is a condition of their entanglement
\autocite[31]{noeEntanglement2023}.

% Another point I want to make to bring in Arendt: that respect I mentioned
% earlier is a respect for the first-order concept. This respect gives the
% second-order concept a kind of authority in Arendt's sense; not violence or
% persuasion, but the understanding that the second-order is something one can
% validly appeal to. The second-order has a normative role regarding the first
% order, and this normativity relies on authority. Maybe I should talk about how
% Noë kinda drops the first/second order language? Argument: an entanglement of
% common and technical realms can explain dogmatic splits in the cognitive
% science of art. Requirements: what is the entanglement? What are the common
% and technical? Right now, I am trying to say what the entanglement is.
% entanglement: first and second order, each shape each other, does not collapse
% concepts. What else? I could go into my more particular understanding of it.
% features: entanglements are recursive; we can find entanglements between two
% concepts, but also within a concept. Leads to concept of domains, which is
% good tr to Arendt. Features: related is n and n+1 orders; we don't know what n
% is, but we know it is not n+1; n may have been m at another time. Features: a
% result is that we can find nth order art. Features: the first order is not an
% actual first order, it is forgetting the second order. Question: if there is
% no "true" first order, then does the first order not actually exist? It is
% essential for the entanglement. Three main features: recursive, domains, truth
% of first order. I wonder if I can think of or find an example of a second
% order thing becoming first order through its relationship with some other
% higher order thing. I want to use the analogy of zooming or a spotlight; when
% we move the spotlight, we change the borders of the entanglement. I'll do
% this: point out a general feature of the entanglement I need, but then
% transition to my stuff. General feature is that entanglement is just a
% relation, it does not necessarily involve any two kinds of concepts.
% Entanglements happen in time, but this does not require a clear origin, maybe?
Dance and dance are cultural practices, so they make for good examples of an
entanglement. By their nature, cultural practices will involve standards
(however fuzzy or implicit) that help us determine what actions do and do not
count as belonging to the practice. When we find that two practices are

relevantly similar, we find it natural to extend the standards of one area to
another. In the case of dance and Dance, the latter's technicality and
artfulness are relevant enough to merit a new category. Nevertheless, we maintain
that dance and Dance are concerned with the same kind of thing, namely,
expressive movement. Both of these views exist in a common understanding of
dancing, but the entanglement makes their relationship explicit.

As is popular to assert nowadays, one could argue that the entanglement of dance
and Dance is best understood in terms of a spectrum. It could be, for instance,
that Dance is dance made technical. Consequently, the entanglement is
unnecessary to understand how these concepts relate to each other; instead, we
only need a spectrum of artfulness or technicality. That dance and Dance exist
along the same spectrum may capture some aspects of their relation. However the
entanglement is partly concerned with our perception of concepts; it starts,
after all, from phenomenology. While we take tools to extend our habitual
selves, we take art (like Dance) to expose, explore, and rearrange us
\autocite[21--22]{noeEntanglement2023}.

Moreover, items on a spectrum may contextualize each other, but they do not have
to change each other. However, an entanglement requires mutual development.
Crucially, insofar as dance is something beyond mere expressive movement, it is
entangled. Because second-order choreography actively loops down to reorganize
our ``spontaneous'' practices, the two cannot be isolated. There is thus no
history of dance outside of its entanglement with Dance
\autocite[32]{noeEntanglement2023}. Yet, if our first-order practices are always
already informed by the second-order, we are left with some critical questions:
what was the first-order all along? Are first-order selves, practices, or
concepts even possible?

It is telling that Noë largely moves away from the language of first- and
second-orders as \textit{The Entanglement} progresses. These terms are
illustrative, but they simplify and distort the entanglement in two ways: first,
the terms ``first-order'' and ``second-order'' imply a chronology. They suggest
a story in which some second-order act of reflection interrupts a pristine,
natural, yet unrefined practice or way of being. However, part of Noë's point is
that no such state exists. Second, and this related to my former concern,
``first'' and ``second'' are absolute terms. In the sense described thus far,
belonging to the first-order could suggest a kind of origin. Despite this, the
entanglement is incompatible with any sort of stable and historical essence
\autocite[32]{noeEntanglement2023}.

To be sure, the language of first- and second-orders is flawed. Regardless, the
source of these flaws is a notable, albeit implicit, feature of the
entanglement: recursivity. As mentioned above, an essential part of going
second-order is putting the first-order on display; in doing so, it ``enables
us to do it all differently'' \autocite[42]{noeEntanglement2023}. This was
apparent in the case of dance and Dance. My contribution, here, is to point out
that Dance's status as ``second-order'' is a relative, rather than absolute or
inherent, property; Dance is only ``second-order'' in relation to dance.
However, nothing about Dance per se is second-order.

For example, consider postmodern art. Within a given artistic practice, one is
likely to encounter postmodernist variations and traditions. Take, for instance,
the example of postmodern choreography. In \textit{Postmodern Dance}, dance
historian Sally Banes argues that postmodern choreography is defined partly by
its relationship with other forms of dance (or, in Noë's terms, Dance). The
relationship she describes is critical and dialectical, with postmodern dance
engaging in an ``anti-modernist, interdisciplinary mingling'' of ``previously
separate spheres'' \autocite[154--155]{banesPostmodern1997}. Notably, as a term,
``postmodern dance'' was first used, not to identify a particular style, but
instead to identify a movement that explicitly rejected modernist styles of
dance \autocite[151]{banesPostmodern1997}.
% I am considering touching on style.

Within Dance, postmodern choreography reacts to other styles of Dance and puts
them on display; it calls on and incorporates other traditions and disciplines,
changing itself in the process. For example, Banes points out that the
politicization of various identities led postmodern dance to foreground and call
on various traditions to create a ``conscious articulation of difference'':

\begin{quote}
    To be sure, some issues of political identity have been and continue to be
    explored and celebrated in dance in a more traditional way ... But in the
    nineties it became clear that many dancers identified themselves as
    bicultural in a specifically avant-garde mode: black and postmodern; Latino
    and postmodern; Asian American and postmodern; gay and postmodern.
    \autocite[154]{banesPostmodern1997}
\end{quote}

Postmodern Dance is informed by the rest of Dance (as well as culture
more broadly), similar to how dance influences choreography as a whole.  Thus,
postmodern choreography goes second-order within Dance, a practice which itself
belongs to the ``second-order.''  This is not to say that modernist, or any
other other styles of Dance, are somehow unthinking or lesser; at a minimum,
modernist choreography and lowercase ``d'' dance are entangled. Moreover, as
previously discussed, ``first-order'' concepts are not naïve. Rather, the point
of this example is to demonstrate that entanglements can be recursive or nested;
the entanglement of dance and Dance was just the beginning.

% I forgot about my attempt to actually define what the first order is...
From the arguments above, I draw two conclusions: first, instead of restricting
ourselves to first- and second-orders, we ought to think of entanglements as
involving an order $n$ and an order $n+1$. It is difficult to pin down the
ultimate origin of any entanglement, if such a thing exists at all. Hence,
labeling something as first-order is a kind of ``second-order'' fallacy where
one takes the substance provided by the first-order for granted without
realizing their position in any other entanglements. In truth, what appears to
be an order $n+1$ practice already belongs to the order $n$ of another
entanglement. For the sake of convenience and legibility, I will use the terms
``lower-order'' and ``higher-order'' instead of ``order $n$'' and ``order
$n+1$,'' respectively. While these terms are less precise, they capture the
concepts' relativity and help separate my interpretation from the simpler first-
and second-order presentation of the entanglement.

% What is my domains argument? Is it an argument by analogy, or am I arguing
% that two things are of the same kind? I want to say something like this: the
% entanglement is not limited to individual, atomic concepts. We might
% intuitively think as dance as its "own thing," but really, dance had a complex
% relationship with Dance, and the two were separate but linked. The problem, I
% think, is assuming that the entanglement has two parts: one, the relation of
% the entanglement; and two, the entangled objects. While this is true, it risks
% leaving out the fact that the objects of the entanglements are themselves
% shaped by internal entanglements; it is entanglements all the way down. So,
% rather than thinking of dance and Dance as individual concepts, they are
% better thought of as realms, or domains. Thus, the objects of an entanglement
% are realms of entanglements. The idea of a realm of entanglement describes a
% lot of Arendt's descriptions of how the public sphere works, and how it
% relates to science, philosophy, and art (but, more importantly, truth in
% general).
%
% So, this is my argument's path: entanglements -> objects of the entanglement
% -> entanglements within those objects -> the public sphere is an entangled
% object -> the exclusive realms of truth are also entangled realms -> the
% public and exclusive realms are entangled with each other. Then, I can finally
% link that to phenomenological and mechanistic perspectives in the cognitive
% science of art. Because I have spent so much time away from this topic, it
% would be a good idea to return to the party example from the beginning.
%
% I have already introduced my claim that entanglements are recursive or nested,
% so I need to get to domains now.
%
% This nesting/recursive stuff is going to be helpful in two ways: one, it lets
% me claim that certain second-order practices can exist and be entangled while
% being in the public sphere, which is itself entangled. I forgot the other one.
% I think it had to do with the kinds of things that can be entangled. Noë talks
% about temporal entanglements.
Second, the members or objects of an entanglement (such as dance and Dance) are
not ``atomic'' concepts; Entangled concepts are internally complex partly
because they themselves contain entanglements. Consequently, entangled concepts
operate more like spaces with their own internal dynamics and less like static
definitions from a dictionary. This structure reveals the kinds of concepts that
can be entangled; it is not limited to individual practices or objects, but
could extend to entire domains or realms of discourse. Further support for this
interpretation comes from Noë's application of the entanglement; for instance,
he argues that science and philosophy are entangled
\autocite[205]{noeEntanglement2023}.

For Noë, science and philosophy are ultimately one epistemic project.  Further,
Noë argues that, in its revolutionary moments, scientists engage in philosophy;
rather than working within a pre-existing framework or developing models,
revolutionary science requires one to change their understanding of a field or
area of research as a whole. For Noë, this kind of work is inherently
philosophical. Moreover, he adds that philosophy also needs science
\autocite[205]{noeEntanglement2023}. Thus, the entanglement of philosophy and
science, on Noë's view, involves undermining an initial understanding of
philosophy and science as distinct disciplines. The co-dependence of philosophy
and science, as well as their overlapping goals, unites them into one entangled
object. Nonetheless, the conceptual distinctions between these disciplines are still
intact; hence, they are entangled insofar as they are separate and unified
\autocite[205]{noeEntanglement2023}.

% Relevant Features of the Public Sphere:
% - Based on discourse and freedom from necessity (derived from Greeks)
% - Foregrounds discourse over truth in a scientific or philosophical sense
% - Primarily contrasted with necessity (not exclusivity; that is new)
% - Originates certain concepts (freedom)
%If entanglements can involve discursive realms, then Arendt's concept of the
%public sphere becomes susceptible to entanglement. If the public sphere admits
%the possibility of its entanglement, then we can begin to see how it shapes
%certain dynamics in cognitive science. This necessitates a closer look at the
%public sphere itself. For Arendt, politics is a specific kind of active social
%arrangement characterized by discourse and freedom from necessity
%\autocite[148]{arendtFuture1968}. The public sphere, or \textit{polis}, is
%where politics happens \autocite[31]{arendtRevolution1990}. Crucially, the
%political realm's focus on discourse changes its relationship with truth and
%opinion.
%
% Instead of the paragraph above, I should use the transition I have given
% myself. I should talk more about how Noë views the entanglement between
% science and philosophy. Then, I can contrast it with a more Arendtian view.
However, as I have previously argued, entanglements are nested; as a result,
there is room to zoom out of this particular entanglement. I contend that, from
this new vantage point, one begins to notice that all of the aforementioned
fields are entangled with a broader sphere of common human affairs. This
entanglement is less like that of philosophy and science, and more like that of
dance and Dance. In the latter case, a kind of ``looping down'' characterizes
the entanglement. The ``looping concept'' is an idea Noë borrows from Ian
Hacking, and it is key to understanding this entanglement. In essence, a looping
concept provides a template, identity, or ideal. These ideals provide normative
standards for what does and does not count as belonging to it. In turn, the
concept ``loops down'' by providing ``self-understanding for those who fall
under them'' \autocite[153]{noeEntanglement2023}.

For example, one's notion of what constitutes good dancing, even in an everyday
sense, might include virtues like grace or expressiveness. Yet, the generation
of such standards requires a kind of higher-order reflection on the habitual act
of dancing. In this case, Dance is looping down to dance. This is the kind of
entanglement I have in mind when I claim that philosophy, science, and even art
are entangled with a broader sphere of human affairs. But what is this sphere,
and what is its entanglement like? To answer these questions, I turn to
political theorist Hannah Arendt. Arendt views common, social human affairs as
political insofar as they are free from the demands of animal necessity, and she
locates this conception of politics in the public sphere
\autocite[157]{arendtPromise2009}.

% TODO: Next I need to develop the exclusive as higher order, explicitly calling
% on Byung-Chul Han. Only after developing the public sphere though.
The public sphere, like the lower-order activity of dance, is close to our
immediate experiences. Consequently, it bears many assumptions that might make
it appear naïve. One notable assumption is that of freedom. Arendt notes that
one encounters freedom, not as an inner quality of their will, but as a result
of their experience in a shared, tangible, outer world. We learn, for instance,
that those bound to necessity or coercion are unfree. One is free, by contrast,
when they assert themselves in the world through ``word and deed''
\autocite[148]{arendtFuture1968}. Crucially, this knowledge is partly implicit;
we do not consciously deliberate to arrive at it. Instead, we recognize it as a
precondition to the political sphere; we hold freedom as a societal standard
without concerning ourselves with its metaphysics
\autocite[152]{arendtFuture1968}.

Nevertheless, according to Arendt, this inner, metaphysical sense of freedom has
its origin in the public sphere. She argues that the problem of free will begin
with the transference of the public concept of freedom to an ``inward domain.''
Once freedom became a topic of philosophical reflection by way of an inward
domain, it lost its public meaning \autocite[146]{arendtFuture1968}. Again,
there is an analogy here between lower-order activities such as dance and the
public sphere; just as dance helps substantiate Dance, the public sphere helps
substantiate philosophy (and science) by providing and originating certain
concepts (freedom, in this case). Here, it is worth noting the epistemic aspects
of this emerging entanglement; the public sphere foregrounds the aforementioned
``word and deed,'' while science and philosophy are more overtly concerned with
truth.

For instance, Arendt argues that factual truths (a kind of empirical, contingent
fact) are, from the political perspective, domineering or anti-political
\autocite[241]{arendtFuture1968}. Similarly, she argues that philosophical truth
(a kind of rational or ``eternal'' truth) becomes opinion once it enters the
public realm \autocite[238]{arendtFuture1968}. To make something political, in
this sense, is to make it subject to debate. Consider the political discourse
surrounding climate change or vaccination; no matter how settled the science is,
the moment one wishes to take action and create policy, they have pushed the
issue into the political realm, which invariably leads to discourse. This move
from one space to another is not merely a move ``from one kind of reasoning to
another but from one way of human existence to another''
\autocite[238]{arendtFuture1968}.

% NOTE: I think this is where I should develop the concept of the exclusive some
% more. I might need to get rid of this paragraph or put one above it.
The public sphere's collective, active, and discursive nature can put it at odds
with truth-oriented disciplines. As Han observes, ``truth is exclusive and
selective'' \autocite[40]{hanSwarm2017}. To form genuine knowledge, one needs
time and the struggle of negativity; one needs a healthy respect for epistemic
authority, as well. Popular discourse often lacks the bearing required for this
kind of engagement. Arendt herself argues that truth-tellers and truth-oriented
institutions must stand outside of politics; the political realm requires
institutions that are outside of its struggles
\autocite[260--261]{arendtFuture1968}. Regardless, as mentioned earlier,
truth-oriented disciplines are still realms of discourse. Noë has already
stressed the entanglement of certain truth-oriented domains (in particular,
science and philosophy). Here, I claim that a broader realm of exclusivity
comprises each of these domains; the already entangled concepts of philosophy
and science are nested within another possible object of entanglement.  Thus,
the public realm's relation to truth is subsumed by its relation to the
exclusive.

% Now I want to show that the public and exclusive are entangled. I can use the
% freedom example from Arendt to show this. There is an analogy between how the
% public and technical realms handled the concept of freedom. The public sphere
% operates as a lower order domain that substantiates the higher order domain of
% the exclusive. Analogy might not be the right word; I don't think this is
% merely "like" an entanglement, I think it is an entanglement. The actual
% process by which a public concept becomes technical is functionalization. This
% could be seen as the inverse of how exclusive/technical concepts become
% opinions or topics of debate in the political realm. Also, this is somewhat
% unrelated, but I think I should talk about the nature of this entanglement
% later; like the ways in which these realms remain separate and connected.
%
% Possibly Relevant Notes:
% - "the formal-functional ambiguity of art necessitates analysis in light of
%   the artist's intention"
% - "things function as art when approached as such"
% - "cognitivist solution to the problem of locating art"
% - "historical definition of art"
% - "institutional definition of art"
% - "artworks gain their meaning by being situated in a network of meanings"
% - "trigger conception of art sees artworks as stimuli that trigger aesthetic
%   responses"
% 
% Okay, I think the freedom example is actually a case of the entanglement not
% working out. Maybe I should have an example of it actually working out? Like
% where the exclusive concept successfully loops down to the lower order, and
% the lower order informs or updates the higher order?
%
% I have a more clear plan: artists are a site of entanglement. This
% entanglement works well because it is bi-directional; there is looping down.
% However, this looping down is not present in cognitive science. Artists are
% indebted to the public sphere; they enrich it.  Also, the public realm is
% still a realm of freedom because of nested entanglements.
Artists are a point of entanglement between the public and exclusive. Arendt
points out that artists, like philosophers and scientists, stand outside the
political realm; being an artist is a mode of ``being alone''
\autocite[259--260]{arendtFuture1968}. Artists must turn their attention away
from the world for the process of creation. Moreover, as Noë points out,
detachment and disinterestedness are key features of the aesthetic attitude
\autocite[188--189]{noeEntanglement2023}. Further, it is apparent that many of
our artistic categories have exclusive or academic origins. Yet, this is only
one part of their entanglement. Arendt notes that being an artist is simply one
mode of being \autocite[259--260]{arendtFuture1968}. Moreover, Noë has already
demonstrated how art makes use of lower orders, as in the case of dance and
Dance.

Thus, insofar as one is an artist, they live in an exclusive domain.
Nonetheless, they call on what the public realm originated. In return, they
enrich the public sphere. Crucially, most are never just artists; they
eventually return to the public sphere and embody a common mode of being.
Notably, Nietzsche has argued that, even when an artist studies history (which
we might say belongs to the realm of the exclusive), they do so with an ``eye
towards life'' \autocite[100--101]{nietzscheUnfashionable1995}. In essence,
artists, at some level, recognize their debt to the political realm and pay it
gladly. Artists are careful with public concepts and remember where they came
from, so we are receptive to the artist's work; we allow it to ``loop down'' and
change us \autocite[153]{noeEntanglement2023}.

% Now I want to talk about bad entanglements. I basically have these examples:
% - The free will debate (from Arendt; also introduces functionalization)
% - Nanay's "technical term" claim (implications and arguments as well)
% - Seeley's cognitivist solution
% - Maybe AI
% - Maybe the party example from the beginning
One might characterize this relationship in terms of respect and authority;
lower-order domains grant higher-order domains their authority insofar as the
latter respects what it pulls from the former. In these terms, a lack of respect
shows up as denying the public sphere's centrality. We see glimpses of this
relationship in Arendt's analysis of the problem of free will. Free will, she
argues, was a concept belonging to politics and interpersonal affairs
\autocite[145]{arendtFuture1968}. One encounters freedom in the public realm;
for example, we take individuals to be responsible for their actions unless
something external makes them unfree. One is unfree, for example, when
restricted by necessity \autocite[148]{arendtFuture1968}. 

Therefore, for Arendt, freedom is something one encounters in the public realm
and in experience. By taking this concept of freedom from the public sphere and
placing it into an ``inward domain,'' it becomes subject to ``self-inspection.''
Self-introspection is an isolated activity, and in it, ``philosophic and
metaphysical questions arise'' \autocite[145]{arendtFuture1968}. Hence, the
problem of freedom is no problem of freedom itself; instead, it is a problem
that arises once one moves the concept from the public sphere to the exclusive
domain (philosophy, in particular). Determinism, despite its force in
philosophic or scientific contexts, has not yet looped down in the same way art
has.

% One thing I should address is why this matters; okay, just let us exclusive
% people do our exclusive thing; who cares about the public sphere? I should
% save this for the end.
Even assuming a deterministic view, one can think they have changed their
actions or thoughts, or that they have been changed by some experience, and
these supposed changes can affect politics; they can be the alleged reasons for
action. In contrast, most still cannot help but take themselves and others to be
free, especially regarding legal and moral issues. The problem of free will,
then, is a problem of respect; the public concept of freedom entered the
exclusive domain, but never honored the original concept. Because of this broken
entanglement, free will in an exclusive sense remains politically impotent.
Here, I argue that cognitive science risks making the same mistake.

% Now, I can finally talk about Nanay. I also want to cover problems with the
% phenomenological approaches that Nanay talks about, as well as Noë's.
% Also, I will need Noë for this point. Nanay says several times that he is not
% talking about a common concept, but Noë can show why this distinction is not
% so clean. Also, one point might be like: can anything be purely exclusive at
% all? Maybe at a glance, but when we are talking about cognition, this is very
% hard to maintain.
In \textit{Mental Imagery: Philosophy, Psychology, Neuroscience}, Bence Nanay
offers an interdisciplinary account of mental imagery. Additionally, he argues
that mental imagery founds many human faculties, including memory and the senses
\autocite[viii]{nanayMental2023}. Nanay's arguments, while interesting,
exemplify some of the concerns presented above. First, Nanay claims that
```Mental imagery' is a technical term'' \autocite[3]{nanayMental2023}. He
repeatedly emphasizes this point, later stating that his ``aim here is not to
capture what the general public means by mental imagery''
\autocite[22]{nanayMental2023}. As a result, Nanay does not think there are
``pre-theoretical considerations that should persuade us to use the term one way
or another''; instead we ought to use the term in ways that are ``theoretically
fruitful'' \autocite[22]{nanayMental2023}.

% Two problems with this first view: general (never a clean distinction here)
% and cog sci specific (cognition is common and entangled). Also, I really need
% to mention that part of Nanay's goal is to further our understanding of the
% mind itself.
In terms of the framework developed thus far, Nanay is claiming that mental
imagery is from the exclusive domain; it is not a public concept. If this is
true, then the concept and those who study it are not indebted to the public
sphere. Hence, it is reasonable to prioritize theoretical fruitfulness above all
else. However, the entanglement of the public and exclusive realms means that
this separation is not so clean, especially in the case of cognitive science.
Scientists, as Arendt has pointed out, are humans, and as such eventually return
to the public sphere \autocite[268--269]{arendtFuture1968}. Humans, insofar as
they are members of a common realm, initiate the process of science; this common
realm is where we find humanistic (but non-scientific) motivators such as one's
values, curiosity, or the meaning of their life.

This view aligns with Noë, who claims that the motivations and tools of science
are not themselves scientific \autocite[209]{noeEntanglement2023}. In fact, this
must be the case; science cannot support itself. As Arendt points out, it is an
ideal of modern science to exclude ``all such anthropocentric, that is, truly
humanistic, concerns'' \autocite[266]{arendtFuture1968}. In my view, this ideal
is what motivates another Arendtian concept, one I call functionalization.
Arendt, in her description of liberal and conservative view of history, 

% --- Works Cited ---
\newpage
\printbibliography

\end{document}
